Vertical shear instability in astrophysical disks: vertically global linear calculations with thermal relaxation and applications to the Solar Nebula

### 2015-03-12 appendix.tex
generalized bcrit (attempt 1)

>>>>

\subsection{Limiting form with real frequencies and $\khat\gg 1$}\label{disp_neut_limit}
For neutral modes with real $\hat{\sigma}=\hat{\omega}$ and large
wavenumber $\khat\gg 1$, the real and imaginary parts of
Eq. \ref{relax_disp} are approximately 
\begin{align}
  &0 =M(M+1) + 4\beta\epsilon q M(M+1)\left(\hat{\omega}\khat\right) 
 +\left[1 +
    \gamma\beta^2\left(1-\gamma\right)(1+2M)^2\right]\left(\hat{\omega}\khat\right)^2
 + 2\epsilon q \gamma\beta \left(\hat{\omega}\khat\right)^3 -  \left(\hat{\omega}\khat\right)^4 
  + \beta^2\gamma^2\hat{\omega}^2
  \left(\hat{\omega}\khat\right)^2,\label{relax_cond1} \\
   &0= \epsilon q M (M+1)\khat +
   \beta(1-\gamma)(1+2M)^2\khat\left(\hat{\omega}\khat\right) 
   + \epsilon q \khat \left(\hat{\omega}\khat\right)^2 -
   2\beta\hat{\omega}\left(\hat{\omega}\khat\right)^2
   - \epsilon q
   \gamma^2\beta^2\hat{\omega}\left(\hat{\omega}\khat\right)^3 
   +
   2\beta\gamma\hat{\omega}\left(\hat{\omega}\khat\right)^4 \label{relax_cond2}. 
\end{align}
These equations are used to derive a critical thermal timescale in
\S\ref{iso_vsi_beta_crit}. For a given $M$, we assume
$|\hat{\omega}\khat|$ remain constant but $\khat\gg 1$ and
$|\hat{\omega}|\ll 1$.  Then for a thin disk $\epsilon \ll 1$,
we neglect the second, fourth and last term in Eq. \ref{relax_cond1};
and neglect the last three terms in Eq. \ref{relax_cond2}. This gives
Eq. \ref{relax_cond_simp1}---\ref{relax_cond_simp2}.

### 2015-03-12 linear_adia.tex
generalized bcrit (attempt 1)

Inserting Eq. \ref{nearly_iso_pert} into Eq. \ref{nearly_iso_explicit}
and keeping only first order terms yield the requirements, after
balancing constants and coefficients of $\zhat^2$, 
% we obtain  
% \begin{align}
%  0 =& \delta v_{z1}^{\prime\prime} - z\left(1 + \ii\epsilon q
%    k\right)\delta v_{z1}^\prime\notag\\
%  &+ \left[2\hat{\sigma}\delta\hat{\sigma}\left(1 + \khat^2\right) +
%    \left(\hat{\sigma}^2 - 1\right)\delta\chi \right.\notag\\
% &\phantom{++} \left. + \zhat^2\left(\khat^2 -
%      \ii\epsilon q \khat\right)\delta\chi\right]\delta v_z\notag\\
%  &+\left[\hat{\sigma}^2\left(1 + \khat^2\right) - \left(1+\ii\epsilon
%      q \khat\right)\right]\delta v_{z1}.\label{nearly_iso4}
% \end{align}
% In Eq. \ref{nearly_iso_pert} and \ref{nearly_iso4}, $\delta v_z$ is to
% a solution to Eq. \ref{nearly_iso_explicit} with 
% $\beta=0$. 
% We could proceed by considering the entire set of polynomial solutions
% for $W$, and hence for $\delta v_z$, as derived in \S\ref{iso_poly}, but it
% is simplest to look at the fundamental mode. 
%Inserting the above expressions for $\delta v_z$, $\delta v_{z1}$ and
%$\hat{\sigma}^2$ into Eq. \ref{nearly_iso4}, then balancing
%coefficients of $\zhat^2$ and constants, we require
\begin{align}
  0 &= 2a + 2\hat{\sigma}\left(1+\khat^2\right)\delta\hat{\sigma} +
  \left(\hat{\sigma}^2 -1\right)\delta\chi,\notag\\
  0&= 2a\left(1+\ii\epsilon q \khat\right) - \left(\khat^2 - \ii\epsilon
    q \khat\right)\delta\chi.
\end{align}

Using the expressions for $\delta\chi$ and $\hat{\sigma}$ we can solve
for $\delta\hat{\sigma}$. This gives 
\begin{align}\label{nearly_iso_dsig}
  \delta \hat{\sigma} =
  -\frac{\ii\left(\gamma-1\right)\hat{k}^2\left(\ii\epsilon
      q - \hat{k}\right)^2}{2\left(1+\ii\epsilon q \hat{k}\right)\left(1+\hat{k}^2\right)^2}\delta\beta.
\end{align}
The imaginary part of Eq. \ref{nearly_iso_dsig} is
\begin{align}
  \delta\hat{\nu} =
  -\frac{\left(\gamma-1\right)\hat{k}^2 \left(\hat{k}^2 -
      2\epsilon^2q^2\hat{k}^2 - \epsilon^2q^2\right)}{2\left(1+\epsilon^2 q^2
      \hat{k}^2\right)\left(1+\hat{k}^2\right)^2}\delta\beta.  
\end{align}
Since $\epsilon \ll 1$, introducing finite cooling $\delta\beta>0$
implies $\delta\hat{\nu} < 0$, i.e. stabilization. Interestingly, for both
$\hat{k}\to0$ and $\hat{k}\to\infty$ we find $\delta\hat{\nu}\to0$, so
stabilization by small finite cooling is ineffective at very large or
very small scales. 
% We plot Eq. \ref{nearly_iso_dsig} in
% Fig. \ref{domegadbeta} with 
% $\epsilon=0.05$, $q=-1.0$ and $\gamma=1.4$. For this disk model the
% optimum wavenumber for stabilization is $\hat{k}\sim 5$---$6$.

% This contrasts to the case without vertical shear
% ($q=0$), in which $\p\hat{\sigma}/\p\beta\to\mathrm{constant}$ as 
% $\hat{k}\to\infty$.

% \begin{figure}
%   \includegraphics[width=\linewidth]{figures/domegadbeta}
%   \caption{Rate of change of the fundamental VSI eigenfrequency
%   $\sigma$ with respect to the introduction of a small but finite
%   cooling time. The plotted quantity is $\p\hat{\sigma}/\p\beta$ at $\beta=0$, evaluated using
%   Eq. \ref{nearly_iso_dsig} with 
%   disk parameters $\epsilon=0.05$, $q=-1$ and $\gamma=1.4$. The real
%   (imaginary) part of $\p\hat{\sigma}/\p\beta$ is shown as the solid
%   (dotted) lines. 
%   \label{domegadbeta}}  
% \end{figure}

@@

Eq. \ref{nearly_iso_explicit} becomes 
\begin{align}
  0 = g^{\prime\prime} - \hat{z}\left(A - 2\alpha\right)g^\prime +
  \left(B + \alpha\right)g.
\end{align}
We seek polynomial solutions 
\begin{align}
  g(\zhat) = \sum_{m=0}^M b_m \zhat^m,
\end{align}
which requires
\begin{align}
  B(\hat{\sigma}) + \alpha(\hat{\sigma}) =
  M\left[A-2\alpha(\hat{\sigma})\right].\label{adia_disp0} 
\end{align}
% We remark that for $q=0$ and $\beta\to\infty$, Eq. \ref{adia_disp0} is
% the same as Eq. 54 in \cite{lubow93} when the low-frequency, Keplerian
% approximation is made in the latter. 
% Eq. \ref{nearly_iso_explicit} is same form
% as the governing equation for the adiabatic case
% (Eq. \ref{adia_iso4}). However, the coefficients $\widetilde{B}$ and $\widetilde{C}$
% have a complicated dependence on $\hat{\sigma}$. 
% Applying the same solution method as in \S\ref{adia_explicit}, we 
% find the adiabatic dispersion relation, 
For ease of analysis, we square Eq. \ref{adia_disp0} to obtain a 
a polynomial in $\hat{\sigma}$,  
\begin{align}
  0 = \sum_{l=0}^{6}c_l\hat{\sigma}^l,\label{relax_disp}
\end{align}
where the coefficients $c_l$ are given in Appendix \ref{relax_coeff}.
The dispersion relation $\hat{\sigma}=\hat{\sigma}(\khat)$ generally
requires a numerical solution. However, for the fundamental mode
($M=0$) some analytic progress can be made, which we consider next.

% It is simplest to solve Eq. \ref{relax_disp} numerically. In
% Fig. \ref{relax_disp_fig} we plot the growth rate of the fundamental
% ($M=0$) VSI mode as a function of $\khat$ for a range of
% dimensionless thermal relaxation timescales $\beta$, in a disk with
% $\epsilon=0.05$, $q=-1$ and $\gamma=1.4$. Increasing $\beta$ even
% slightly above zero significantly reduces the growth rates for
% $\khat\gg 1$. (There is little effect at small $\khat$ but this case is
% not of interest because the local model breaks down.) Thus, 
% a growing fundamental VSI mode exists only for nearly
% isothermal perturbations ($\beta\ll 1$).  The plot is also consistent with our previous
% discussion that there exists an intermediate wavenumber for which
% finite thermal relaxation has maximal effect (for small $\beta$).

% \begin{figure}
%   \includegraphics[width=\linewidth,clip=true,trim=0cm 0.0cm 0cm 0cm]{figures/rate_theory_grow_relax}
% %  \includegraphics[width=\linewidth,clip=true,trim=0cm 0cm 0cm 1cm]{figures/rate_theory_grow_relax2}
%   \caption{Growth rate of the fundamental VSI mode in a disk with
%     dimensionless thermal relaxation timescales
%     $\beta\in[10^{-3},1]$.  Other disk parameters are
%     $\epsilon=0.05$, $q=-1$ and $\gamma=1.4$. The growth rates are
%     calculated from the dispersion relation Eq. \ref{relax_disp}. 
%     \label{relax_disp_fig}}  
% \end{figure}

% ate_theory, eps=0.05, smallq=-1d0, gmma=1.4, bmax=1.0, ncases=11,
%mmode=0.0, root=1, legend=[0.102,0.14,5.4,0.355], yrange=[0,6]

\subsection{Upper limit on the thermal relaxation timescale for the
  fundamental VSI mode}\label{iso_vsi_beta_crit}

Here we estimate the maximum thermal relaxation timescale
$\beta$ that allows the fundamental VSI mode for $\khat\gg1$.   
% Notice in Fig. \ref{relax_bcrit} the upper limit on $\beta$ for the
% fundamental isothermal VSI tends to a constant for large
% $\khat$. Using this clue, we can calculate this critical $\beta$ by
% considering $\khat\to\infty$. We proceed as follows. 
At marginal stability, the eigenfrequency $\hat{\sigma}=\hat{\omega}$
is real. The dispersion relation for the fundamental mode is then
\begin{align}\label{relax_disp_fund}
  0 = \sum_{l=1}^{6}c_l\hat{\omega}^l \quad \text{for $M=\hat{\nu}=0$}.  
\end{align} 
Taking the real and imaginary parts of Eq. \ref{relax_disp_fund} and considering 
$\khat\gg1$, we find
\begin{align}
  0 =& \left[1 + \gamma\beta^2\left(1-\gamma\right)\right] + 2\epsilon q
  \gamma\beta (\hat{\omega}\khat) -  (\hat{\omega}\khat)^2 \notag\\
  &+ \beta^2\gamma^2\hat{\omega}^2 (\hat{\omega}\khat)^2,\label{relax_cond1}\\
  0=& \beta(1-\gamma)\khat^2 + \epsilon q \khat^2 (\hat{\omega}\khat)
  - 2\beta (\hat{\omega}\khat)^2 - \epsilon q \gamma^2\beta^2 (\hat{\omega}\khat)^3 \notag\\
    &+ 2\beta\gamma(\hat{\omega}\khat)^4.  
\label{relax_cond2}
\end{align}
This is a pair of simultaneous equations for
$\hat{\omega}$ and $\beta$. Now, low-frequency axisymmetric waves in
the absence of vertical shear are stable and  satisfy
$\hat{\omega}\propto \khat^{-1}$ (Appendix \ref
{stable_novshear}, Eq. \ref{iso_disp_full}).  We are thus motivated to
seek solutions to Eq. \ref{relax_cond1}---\ref{relax_cond2} with  
% we wish to seek a criterion independent of k 
% \begin{align}
%   \khat \to \infty, \quad \hat{\omega}\to 0 ,\quad \hat{\omega} \khat\text{ finite}.
%\end{align}
\begin{align}
  \khat \gg1, \quad |\hat{\omega}|\ll 1 ,\quad
  |\hat{\omega}\khat|=O(1). 
\end{align}
Then
\begin{align}
  \hat{\omega}\khat = \frac{(\gamma-1)\beta}{\epsilon q}
\end{align}
from Eq. \ref{relax_cond2}, which implies, from Eq. \ref{relax_cond1}
that
\begin{align}\label{beta_crit0}
  \beta = \frac{1}{(\gamma-1)}\left[\frac{1}{\left(\epsilon
        q\right)^2} - \frac{\gamma}{(\gamma-1)}\right]^{-1/2} 
\end{align}
at marginal stability for perturbations with large $\khat$.

From our discussion in \S\ref{relax_pert}, which indicate introducing
a finite thermal relaxation is stabilizing, we expect
Eq. \ref{beta_crit0} is an upper limit. For a thin  
disk $\epsilon\ll 1$, we thus infer 
\begin{align}\label{iso_vsi_cond}
  \beta \lesssim \frac{|\epsilon q|}{\gamma-1} \equiv
  \beta_\mathrm{crit} 
\end{align}
is required for the fundamental VSI to operate. That is, when
$\beta<\beta_\mathrm{crit}$, perturbations are  effectively isothermal. 
We will confirm Eq. \ref{iso_vsi_cond} numerically in
\S\ref{bcrit_num_test}.

Rapid thermal relaxation is required to overcome a stabilizing
vertical entropy gradient \citep{goldreich67,urpin98,urpin03}, but
this conclusion was reached in these studies by considering
vertically-localized disturbances. % , although a definitive timescale
                                % was not presented.  
By contrast, our Eq. \ref{iso_vsi_cond} quantifies this requirement
for vertically global disturbances (i.e. the fundamental mode). We see
that in a thin disk, a very short thermal timescale
 is required ($\beta_\mathrm{crit}\ll 1$) because
$\beta_\mathrm{crit}\propto \epsilon$. 
This suggests that
finite thermal relaxation rapidly stabilizes the VSI.

>>>>

Inserting Eq. \ref{nearly_iso_pert} into Eq. \ref{nearly_iso_explicit}
and keeping only first order terms yield the requirements, after
balancing constants and coefficients of $\zhat^2$,

\begin{align}
  0 &= 2a + 2\hat{\sigma}\left(1+\khat^2\right)\delta\hat{\sigma} +
  \left(\hat{\sigma}^2 -1\right)\delta\chi,\notag\\
  0&= 2a\left(1+\ii\epsilon q \khat\right) - \left(\khat^2 - \ii\epsilon
    q \khat\right)\delta\chi.
\end{align}

Using the expressions for $\delta\chi$ and $\hat{\sigma}$ we can solve
for $\delta\hat{\sigma}$. This gives 
\begin{align}\label{nearly_iso_dsig}
  \delta \hat{\sigma} =
  -\frac{\ii\left(\gamma-1\right)\hat{k}^2\left(\ii\epsilon
      q - \hat{k}\right)^2}{2\left(1+\ii\epsilon q \hat{k}\right)\left(1+\hat{k}^2\right)^2}\delta\beta.
\end{align}
The imaginary part of Eq. \ref{nearly_iso_dsig} is
\begin{align}
  \delta\hat{\nu} =
  -\frac{\left(\gamma-1\right)\hat{k}^2 \left(\hat{k}^2 -
      2\epsilon^2q^2\hat{k}^2 - \epsilon^2q^2\right)}{2\left(1+\epsilon^2 q^2
      \hat{k}^2\right)\left(1+\hat{k}^2\right)^2}\delta\beta.  
\end{align}
Since $\epsilon \ll 1$, introducing finite cooling $\delta\beta>0$
implies $\delta\hat{\nu} < 0$, i.e. stabilization. Interestingly, for both
$\hat{k}\to0$ and $\hat{k}\to\infty$ we find $\delta\hat{\nu}\to0$, so
stabilization by small finite cooling is ineffective at very large or
very small scales.

@@

Eq. \ref{nearly_iso_explicit} becomes 
\begin{align}
  0 = g^{\prime\prime} - \hat{z}\left(A - 2\alpha\right)g^\prime +
  \left(B + \alpha\right)g.
\end{align}
We seek polynomial solutions 
\begin{align}
  g(\zhat) = \sum_{m=0}^M b_m \zhat^m,
\end{align}
which requires
\begin{align}
  B(\hat{\sigma}) + \alpha(\hat{\sigma}) =
  M\left[A-2\alpha(\hat{\sigma})\right].\label{adia_disp0} 
\end{align}
For ease of analysis, we square Eq. \ref{adia_disp0} to obtain a 
a polynomial in $\hat{\sigma}$,  
\begin{align}
  0 = \sum_{l=0}^{6}c_l\hat{\sigma}^l,\label{relax_disp}
\end{align}
where the coefficients $c_l$ are given in Appendix \ref{relax_coeff}.
The dispersion relation $\hat{\sigma}=\hat{\sigma}(\khat)$ generally
requires a numerical solution. However, simple solutions may be
obtained in limiting cases which we consider below.

% However, for the fundamental mode
% ($M=0$) some analytic progress can be made, which we consider next.

\subsection{Upper limit on the thermal relaxation timescale for the
  VSI}\label{iso_vsi_beta_crit}
Here we estimate the maximum thermal relaxation timescale
$\beta$ that allows the VSI. We consider wavenumbers such that
$\khat^2\gg M+1$ which, as we will find, correspond to low frequency
modes.

%At marginal stability, the eigenfrequency $\hat{\sigma}=\hat{\omega}$ is real.  
%This is a pair of simultaneous
%equations for $\hat{\omega}$ and $\beta$. To proceed, we
%consider further limits.

Our starting point is Eq. \ref{relax_cond1}---\ref{relax_cond2} which
approximates the dispersion relation Eq. \ref{relax_disp} at marginal
stability with $\khat\gg 1$. We consider modes with $M=0$ (the
fundamental mode) or  $M=O(1)$ and low frequency $|\hat{\omega}|\ll
1$ such that $|\hat{\omega}\khat|$ is $O(1)$ because $\khat\gg 1$. We
also assume $|q|$ and $\beta$ are $O(1)$ or less. For a thin disk
($\epsilon \ll 1$), we have approximately
\begin{align}
 0 = &M(M+1) + \left[1 +
    \gamma\beta^2\left(1-\gamma\right)(1+2M)^2\right]\left(\hat{\omega}\khat\right)^2\notag\\
   &-  \left(\hat{\omega}\khat\right)^4,\label{relax_cond_simp1}\\
   0= &M(M+1) + \frac{\beta}{\epsilon q} (1-\gamma)(1+2M)^2
   \left(\hat{\omega}\khat\right) + \left(\hat{\omega}\khat\right)^2. \label{relax_cond_simp2}
\end{align}
(We explain this in Appendix \ref{disp_neut_limit}.)

Eq. \ref{relax_cond_simp1}---\ref{relax_cond_simp2} is a pair of
simultaneous equations for $\hat{\omega}$ and the critical thermal
timescale $\beta$ for marginal stability. If $\beta\ll 1$,
then a simple solution to Eq. \ref{relax_cond_simp1} is 
\begin{align}
  \left(\hat{\omega}\khat\right)^2 \simeq M+1, 
\end{align}
which is the dispersion relation for low-frequency waves in vertically
isothermal disks without vertical shear (see Appendix
\ref{stable_novshear}). Then  
\begin{align}\label{bcrit_gen}
  \beta = \frac{\epsilon|q|}{(\gamma - 1)}
  \frac{(1+M)^{3/2}}{(1+2M)^2} \leq \beta_\mathrm{crit} 
\end{align}
where 
\begin{align}\label{iso_vsi_cond}
  \beta_\mathrm{crit}  \equiv \frac{\epsilon|q|}{\gamma-1}
\end{align}
is the critical thermal timescale for the fundamental mode
($M=0$). However, according to Eq. \ref{bcrit_gen}  the critical
thermal timescale decreases with increasing  $M$. We thus expect
higher order modes to be stabilized more rapidly by finite thermal
relaxation $\beta$. When $\beta>\beta_\mathrm{crit}$, all modes
(satisfying the above assumptions) are stabilized. We can interpret
$\beta_\mathrm{crit}$ as the thermal timescale below which
perturbations are effectively isothermal to allow the VSI.  We will confirm
Eq. \ref{iso_vsi_cond} numerically in \S\ref{bcrit_num_test}.

(We remark that the critical thermal timescale $\beta_\mathrm{crit}$
for the fundamental mode may be obtained more readily with fewer
assumptions by setting $M=0$ in
Eq. \ref{relax_cond1}---\ref{relax_cond2} from the onset. )

Rapid thermal relaxation is required to overcome a stabilizing
vertical entropy gradient \citep{goldreich67,urpin98,urpin03}. This 
conclusion was reached in these studies by considering
vertically-localized disturbances. % , although a definitive timescale
                                % was not presented.  
By contrast, our Eq. \ref{iso_vsi_cond} quantifies this requirement
for vertically global disturbances. We see that in a thin disk, a very
short thermal timescale is required ($\beta_\mathrm{crit}\ll 1$)
because $\beta_\mathrm{crit}\propto \epsilon$. 
This suggests that finite thermal relaxation rapidly stabilizes the
VSI.

% Here we estimate the maximum thermal relaxation timescale
% $\beta$ that allows the fundamental VSI mode for $\khat\gg1$.

% At marginal stability, the eigenfrequency $\hat{\sigma}=\hat{\omega}$
% is real. The dispersion relation for the fundamental mode is then
% \begin{align}\label{relax_disp_fund}
%   0 = \sum_{l=1}^{6}c_l\hat{\omega}^l \quad \text{for $M=\hat{\nu}=0$}.  
% \end{align} 
% Taking the real and imaginary parts of Eq. \ref{relax_disp_fund} and considering 
% $\khat\gg1$, we find
% \begin{align}
%   0 =& \left[1 + \gamma\beta^2\left(1-\gamma\right)\right] + 2\epsilon q
%   \gamma\beta (\hat{\omega}\khat) -  (\hat{\omega}\khat)^2 \notag\\
%   &+ \beta^2\gamma^2\hat{\omega}^2 (\hat{\omega}\khat)^2,\label{relax_cond1}\\
%   0=& \beta(1-\gamma)\khat^2 + \epsilon q \khat^2 (\hat{\omega}\khat)
%   - 2\beta (\hat{\omega}\khat)^2 - \epsilon q \gamma^2\beta^2 (\hat{\omega}\khat)^3 \notag\\
%     &+ 2\beta\gamma(\hat{\omega}\khat)^4.  
% \label{relax_cond2}
% \end{align}
% This is a pair of simultaneous equations for
% $\hat{\omega}$ and $\beta$. Now, low-frequency axisymmetric waves in
% the absence of vertical shear are stable and  satisfy
% $\hat{\omega}\propto \khat^{-1}$ (Appendix \ref
% {stable_novshear}, Eq. \ref{iso_disp_full}).  We are thus motivated to
% seek solutions to Eq. \ref{relax_cond1}---\ref{relax_cond2} with  
% % we wish to seek a criterion independent of k 
% % \begin{align}
% %   \khat \to \infty, \quad \hat{\omega}\to 0 ,\quad \hat{\omega} \khat\text{ finite}.
% %\end{align}
% \begin{align}
%   \khat \gg1, \quad |\hat{\omega}|\ll 1 ,\quad
%   |\hat{\omega}\khat|=O(1). 
% \end{align}
% Then
% \begin{align}
%   \hat{\omega}\khat = \frac{(\gamma-1)\beta}{\epsilon q}
% \end{align}
% from Eq. \ref{relax_cond2}, which implies, from Eq. \ref{relax_cond1}
% that
% \begin{align}\label{beta_crit0}
%   \beta = \frac{1}{(\gamma-1)}\left[\frac{1}{\left(\epsilon
%         q\right)^2} - \frac{\gamma}{(\gamma-1)}\right]^{-1/2} 
% \end{align}
% at marginal stability for perturbations with large $\khat$.

% From our discussion in \S\ref{relax_pert}, which indicate introducing
% a finite thermal relaxation is stabilizing, we expect
% Eq. \ref{beta_crit0} is an upper limit. For a thin  
% disk $\epsilon\ll 1$, we thus infer 
% \begin{align}\label{iso_vsi_cond}
%   \beta \lesssim \frac{|\epsilon q|}{\gamma-1} \equiv
%   \beta_\mathrm{crit} 
% \end{align}
% is required for the fundamental VSI to operate. That is, when
% $\beta<\beta_\mathrm{crit}$, perturbations are  effectively isothermal. 
% We will confirm Eq. \ref{iso_vsi_cond} numerically in
% \S\ref{bcrit_num_test}.
